---
title: "generate_aRt"
author: "Jacques Serizay"
date: 2020-11-26T00:00:00
slug: "" 
tags: 
    - R
    - 'Data Viz'
categories: 
    - R
    - 'Data Viz'
showpagemeta: false
showcomments: false
draft: false 
comments: false
output: 
    blogdown::html_page:
        highlight: "tango" 
        toc: true
        toc_depth: 1
        number_sections: false
        fig_width: 12
---

## Setting the scene 

Here is an attempt to do some generative art. I got a lot of inspiration from the following sources:
 
- https://medium.com/@vitgabrhel/getting-started-with-generative-art-in-r-3bc50067d34b
- https://github.com/djnavarro/jasmines
- https://github.com/cutterkom/generativeart
- http://www.citizen-statistician.org/2020/05/dipping-my-toes-in-generative-art-with-my-sister/
- https://www.r-bloggers.com/2020/05/generative-art-let-your-computer-design-you-a-painting/
- https://flowingdata.com/2019/09/27/detailed-generative-art-in-r/
- https://www.data-imaginist.com/art

Some `R` packages for this project: 

```{r, eval = FALSE}
remotes::install_github("thomasp85/ambient")
remotes::install_github("cutterkom/generativeart")
remotes::install_github("djnavarro/jasmines")
```

Loading libraries... 

```{r}
require(tidyverse)
require(jasmines)
```

---

## Trying `jasmines` package out

```{r}
d <- use_seed(1) %>%
    entity_droplet(grain = 1000) %>% 
    unfold_warp(
        iterations = 1,
        scale = .1
    ) %>%
    unfold_tempest(iterations = 30)
style_ribbon(data = d)
```

---

## A more personnal project: a piece of art for everybody 

The generative art packages that are out there are a tiny bit too obscure for me. This most likely comes from the fact that I have little knowledge in the maths behind the noise generative functions from `ambient`. So I decided to write my own package to create generative art. 

The aim here is to create a piece of art corresponding to a specific individual, based on two different specific values: 

- Given name 
- D.O.B

`name` will be used to pick a random seed. `dob` will be used to pick a spot in a genome. 

The package I wrote to generate this artistic "view" of someone's genome is called `dnaRt`.

```{r, eval = FALSE}
remotes::install_github('js2264/dnaRt')
library(dnaRt)
```

```{r}
name='jacques'
dob="20/06/1992"
```

Then I create a "dnart" project as follows:

```{r echo = FALSE}
devtools::load_all('~/Documents/Projects/dnaRt/')
dnart_project <- dnart(
	folder = 'data',
	given = name, 
	dob = dob, 
    data = sample_data
)
```

```{r eval = FALSE}
dnart_project <- dnart(
	folder = 'data',
	given = name, 
	dob = dob
)
```

I can then plot an artistic plot of the sequences randomly picked by my package and displayed as a network: 

```{r}
dnart_project <- dnart_project %>% 
	plotArt(
		ratio = 1.66, 
		zoom = 3, 
		orientation = 'landscape', 
		file = 'graph.pdf'
	)
dnart_project$plot
```

---

## Session info 

```{r}
devtools::session_info()
```